{\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over mathematical content in digital libraries

### 2015-01-31 jcdl2015/paper/main.tex
Fixed a typo in conclusions, played with the size of the screenshots, managed to get them bigger without adding extra pages.

\begin{figure}
\centering
\begin{minipage}{.27\textwidth}
  \includegraphics[width=0.9\linewidth]{images/figures/input_interface.png}
  \captionof{figure}{Input interface.}
  \label{fig:test1}
\end{minipage}%
\begin{minipage}{.27\textwidth}
  \includegraphics[width=0.9\linewidth]{images/figures/results_interface.png}
  \captionof{figure}{Result page.}
  \label{fig:test2}
\end{minipage}
\end{figure}

@@

In this demonstration, we presented an important limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical to our system. We presented our approach to model mathematical equations in terms of two different types of features. How we extended the Lucene/Solr Framework to handle our specific type of content and how through the Mathematica CAS, we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, and use them to improve the quality of the results. Finally we presented our integration mechanism with the Invenio software through the solarpy library.

>>>>

\begin{figure}
\centering
\begin{minipage}{.37\textwidth}
  \includegraphics[width=0.95\linewidth]{images/figures/input_interface.png}
  \captionof{figure}{Input interface.}
  \label{fig:test1}
\end{minipage}%
\end{figure}

\begin{figure}
\centering
\begin{minipage}{.37\textwidth}
  \includegraphics[width=0.95\linewidth]{images/figures/results_interface.png}
  \captionof{figure}{Result page.}
  \label{fig:test2}
\end{minipage}
\end{figure}

@@

In this demonstration, we focused on a limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical content. We presented our approach to model mathematical equations in terms of two different types of features. We extended the Lucene/Solr framework to handle specific type of content and through the Mathematica CAS we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, improving the quality of the results. Finally we presented our integration mechanism with the Invenio software through the solarpy library.
